R Notebook

### 2020-02-13 src/comb-maxent.Rmd
minor change to package

  
```{r pre-install & load packages, include=FALSE}
options(java.parameters = "-Xmx2g" )#needs to run before dismo loaded - boosts memory for java to 1g
packages <- c("dismo", "stringr", "rJava", "raster", "ecospat", "bossMaps", "lattice", "tidyr", "enmSdm", "ggplot2", "plyr", "reshape2", "tidyverse", "patchwork", "purrr")
source("../src/ipak.R")
ipak(packages)
```

@@

# rename the months so they are capitalised
permu$Month <- capitalize(permu$Month)
# jackk$Month <- capitalize(jackk$Month)

@@

```{r permulation plot}
permu <- read.csv("../output/maxent/models/test-comb/permutation_avg.csv")

>>>>

  
```{r pre-install & load packages, include=FALSE}
options(java.parameters = "-Xmx2g" )#needs to run before dismo loaded - boosts memory for java to 1g
packages <- c("dismo", "stringr", "rJava", "raster", "ecospat", "bossMaps", "lattice", "tidyr", "enmSdm", "ggplot2", "plyr", "reshape2", "tidyverse", "patchwork", "purrr", "Hmisc")
source("../src/ipak.R")
ipak(packages)
```

@@

# rename the months so they are capitalised

permu$Month <- capitalize(permu$Month)
# jackk$Month <- capitalize(jackk$Month)

@@

```{r permulation plot}
library(cowplot)
permu <- read.csv("../output/maxent/models/test-comb/permutation_avg.csv")
